### 2020-12-11 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd
condensed phenological results

(*most or all of this should be cut-- first paragraph too detailed for Nature, and we want minimal comparison of ring vs diffuse porous*)

Across all trees and years at SCBI, 
25% of annual growth was achieved on May 20 ($DOY_{25}$=139), 
50% on June 12 ($DOY_{50}$=162), 
and 75% on July 5 ($DOY_{75}$=185), 
for an average peak growing season length of 45 days. 
Maximum growth rate occurred just one day after $DOY_{50}$ on June 13 ($DOY_{max}$=163). 
At Harvard Forest,
25% of annual growth was achieved on June 1 ($DOY_{25}$=151), 
50% on June 23 ($DOY_{50}$=173), 
and 75% on July 14 ($DOY_{75}$=194), 
for an average peak growing season length of 43 days. 
Maximum growth rate occurred on June 24 ($DOY_{max}$=174).

At both sites, growth phenology differed between ring- and diffuse- porous species (Fig. `r growth_curves_all`, Table `r mean_growth_parameters_table`). 
Specifically, ring-porous species began growing earlier, reaching the $DOY_{25}$ benchmark `r 154-123` days earlier at SCBI and `r 164-132` days earlier at Harvard Forest. 
Growth of ring-porous species was spread out over a longer growing season, with average $L_{PGS}$ of ring-porous species being 21 days longer at SCBI and 19 days longer at Harvard Forest. 
Growing season length was similar across sites, with $L_{PGS}$ being, on average, only two days longer at SCBI for ring-porous species and <1 day longer for diffuse-porous species.

>>>>

(*most or all of this should be cut-- first paragraph too detailed for Nature, and we want minimal comparison of ring vs diffuse porous*)
Growth milestones were achieved earlier at SCBI than at Harvard Forest (average difference: #-# days) and differed between ring- and diffuse-porous species (Fig. `r growth_curves_all`, Table `r mean_growth_parameters_table`).
Across all trees and years, $DOY_{25}$ occurred on day 139 (May 20) at SCBI and day 151 (June 1) at Harvard Forest, while $DOY_{75}$ occurred on day 139 (May 20) at SCBI and day 151 (June 1) at Harvard Forest.
Ring-porous species began growing earlier, reaching the $DOY_{25}$ benchmark earlier (by `r 154-123` days at SCBI and `r 164-132` at Harvard Forest), and their growth was spread out over a longer growing season (average $L_{PGS}$ 21 and 19 days longer at SCBI and Harvard Forest, respectively). 
Growing season length was similar across sites, with $L_{PGS}$ being, on average, only two days longer at SCBI for ring-porous species and <1 day longer for diffuse-porous species.
